### 2024-07-30 paper/supplementary.tex
submitted

\newcommand{\SuppCaption}[2]{\noindent\boldblue{{#1}} {#2}\footnotesize}
\newcommand{\SectionHeader}[1]{\noindent\textbf{\Large\textcolor{mydarkblue}{#1}}\normalsize }
\newcommand{\SubSectionHeader}[1]{\noindent\Large{\textcolor{mydarkblue}{#1}}\normalsize }

@@

\abovedisplayskip = 10.0pt plus 2.0pt minus 20.0pt
\belowdisplayskip = 10.0pt plus 2.0pt minus 20.0pt
\abovedisplayshortskip = 0.0pt plus 20.0pt
\belowdisplayshortskip = 9pt plus 3pt minus 20pt

@@

\noindent\textbf{\large\textcolor{mydarkblue}{Supplementary A: High Variance Results}}
\begin{figure}[H]
    \centering
    \includegraphics[scale =1]{figures/exp1_movement_onset_panel.png}
    \renewcommand\figurename{Supplementary Figure}
    \caption{\textbf{Timing Behaviour.} A) Average participant movement onset (y-axis) for each experimental condition (x-axis). We found a significant main effect of stimulus movement onset mean (F[1.55,29.48] = 4.36, p = 0.030) and variance (F[1.00,19.00], p = 0.017)) on participant movement onset. There was no significant interaction (F[1.66,31.47], p = 0.565) B) Corresponding participant movement onset (y-axis) for the three different mean stimulus onsets (x-axis) when collapsed across variance. During the early mean conditions, participants had a high probability of reacting to the stimulus and reaching a target within the time constraint. For the middle mean conditions, participants often waited longer to react and had a later guess than the early mean conditions. Waiting longer to react and/or late guessing led to later movement onset. In the late mean condition, participants waited to react to the stimulus, but ended up guessing a majority of the time (see Supplementary Figure 6). The combination of waiting for the stimulus and eventually guessing, led to an earlier movement onset compared to the middle mean condition. For both the middle mean and late mean conditions, late guessing often led to indecisions (see \boldblue{Fig. 2}). C) Participant movement onset standard deviation (y-axis) for each experimental condition (x-axis). We found a significant main effect of mean (F[1.38, 26.28], p = 0.018) and variance (F[1.00,19.00], p < 0.001) on participant movement onset standard deviation There was no significant interaction between stimulus movement onset mean and variance (F[1.98, 37.58], p = 0.097) D) Corresponding participant movement onset standard deviation (y-axis) for the three different mean onsets (x-axis), when collapsed across variance. In the late mean conditions, waiting to react and then guessing led to a larger movement onset standard deviation compared to the early mean and middle mean conditions. Box and whisker plots display the 25th, 50th, and 75th percentiles. Open gray circles and connecting lines represent individual data.}
\end{figure}

\begin{figure}[H]
    \centering
    \includegraphics[scale = 1]{figures/exp1_score_metrics_panel.png}
    \renewcommand\figurename{Supplementary Figure}

    \caption{\textbf{Trial Outcomes.} \textbf{A)} Indecisions (\%) \textbf{B)} Wins (\%), and \textbf{C)} Incorrects (\%) for each condition. \textbf{A)} We found that the middle mean low variance and \emph{late mean low variance} condition had a significantly greater number of indecisions compared to the \emph{early mean low variance} condition. That is, in the middle mean low variance and \emph{late mean low variance} conditions, participants often waited to react to the stimulus but ended up guessing late. These late guesses often led to indecisions. \textbf{B)} Interestingly, we also found that the average win percentage (41\%) was significantly below the 50\% chance level (p < 0.001) in the \emph{late mean low variance} condition, clearly demonstrating suboptimal behaviour. Critically, participants would have earned more points if they had simply guessed early on all trials, rather than attempting to react to the stimulus. Collectively, these results show that participants were suboptimal decision makers that led to excessively indecisive behaviour.}
\end{figure}

\vspace{2mm}
\noindent\textbf{\large\textcolor{mydarkblue}{Supplementary B: Optimal Models}}

We tested three different models to investigate the ability of participants to maximize reward during \boldblue{Experiment 1}: i) No Switch Time Model, ii) Full Switch Time Model and iii) Partial Switch Time Model (\boldblue{Fig. 2}). Each model represents a different hypothesis on how humans time their decisions, which we address further below. Intuitively, participants should react to the stimulus on trials where it moved earlier in time and guess on trials where it moved later in time. That is, reacting to early stimulus movement onsets ensures they can select the correct target. Likewise, guessing on late stimulus movement onsets affords the participant a 50\% chance of selecting the correct target. However, if participants wait too long to react to a late stimulus movement onset, then they might make too many indecisions and fail to maximize reward.
We modelled the time to switch from reacting to guessing as an optimal transition problem. This differs from past models that have used a similar Bayesian framework, which has beenused to determine reach aim \autocite{trommershauser_statistical_2003} and reach timing \autocite{hudson_optimal_2008}. Here a model represents a decision-maker that selects a transition time, $\tau$. This transition time determines when to stop waiting to react to the stimulus and switch to guessing one of the two targets. The optimal transition time is determined from a decision policy that maximizes reward, given task constraints (i.e. stimulus movement onset distribution and time constraint), and knowledge of sensorimotor delays and uncertainties.

@@

\vspace{2mm}
\noindent \textbf{General Formulation for the Models}

\noindent We begin by defining the general normal probability density function and cumulative density function:

% Define pdf and cdf
\begin{equation}
    X\sim\mathcal{N}(\mu,\sigma)
\end{equation}
\begin{equation}
    f_{X}(x; \mu, \sigma) = \frac{1}{\sigma\sqrt{2\pi}}e^{-\frac{1}{2}(\frac{x-\mu}{\sigma})^2}
\end{equation}
\begin{equation}
    F_{X}(b) = P(X \leq b) = \int_{-\infty}^{b} f_{X}(x; \mu, \sigma)dx
\end{equation}

@@

Next we define the mean and standard deviation of the participant movement onset separately for reaction decisions and guess decisions. We begin by defining $S$ as the random variable drawn from the stimulus’s movement onset distribution (\textbf{Eq. 4}) and $T$ as the random variable drawn from the transition time distribution (\textbf{Eq. 5}).

% Define random variables S and T
\begin{align}
    S & \sim\mathcal{N}(\mu_{S},\sigma_{S}) \\
    T & \sim\mathcal{N}(\tau,\sigma_{\tau})
\end{align}

Consider $s$ and $t$ as the realizations of random variables $S$ and $T$ for a single trial. On any specific trial, a decision-maker will react if the stimulus movement onset is before the transition time (i.e., $s<t$). Conversely, the decision-maker will guess at the transition time if the stimulus has not moved by the transition time (i.e., $s>t$). Thus, the probability that a participant will react or guess depends on the participants choice of a transition time $\tau$. Specifically, the probability that the participant will react is the probability that the random variable A is less than T.

% Define prob react and guess
\begin{equation}
    P(React|\tau) = P(T>S)
\end{equation}

Since the participants can only react or guess, the probability of guessing is simply one minus the probability of reacting.

\begin{equation}
    P(Guess|\tau) = P(T<S)
\end{equation}

As a result, a decision-maker only reacts to the portion of the stimulus’s distribution that is prior to their transition time. Thus, the participant reacts to a truncated distribution of the stimulus movement onset.
The truncated stimulus movement onset distribution is generated from only taking the random variable $S$ if it is less than the random variable $T$. We can then define an indicator function ($\mathbbm{1}_{s<t}$), which is equal to one if the realized value $s$ is less than $t$ and zero otherwise:

% Define indicator function 
\begin{align}
     & \mathbbm{1}_{s<t} =
    \begin{cases}
        1 & \text{if } s < t, \\
        0 & \text{otherwise.}
    \end{cases}
\end{align}

The mean of the truncated stimulus movement onset distribution ($\mu_{S_{react}}$) can be calculated by combining the indicator function and the method of moments. We start by calculating the expected value of the random variable $S$, which is the integral from $-\infty$ to $\infty$ of the value $s$ multiplied by the probability density function $f_{S}(s)$.

% Define expected value
\begin{equation}
    \mu_{S} = \mathbb{E}[S] = \int_{-\infty}^{\infty}s \cdot f_{S}(s)ds
\end{equation}

Note that the expected value of the full stimulus movement onset distribution defined here is equivalent to the mean of the distribution. For the truncated stimulus movement onset distribution, we only take values $s$ if they are less than $t$. Since the inclusion of $s$ depends on $t$, we calculate the mean of the truncated stimulus movement onset distribution by integrating over every possible combination of $s$ and $t$. Inside the double integral, we multiply the realized value $s$ by its probability density function (i.e., $f_{S}(s)$). We also multiply the probability density function for $t$ (i.e., $f_{T}(t)$) and the indicator function ($\mathbbm{1}_{s<t}$). Since this double integral multiplies two gaussian probability density functions and only sums values if $s$ is less than $t$, we must normalize by dividing by the probability that A is less than T. The mean (first moment) of the truncated stimulus movement onset distribution is

% Define Cutoff react mean 
\begin{equation}
    \mu_{S_{react}} = \dfrac{\int_{-\infty}^{\infty}  \int_{-\infty}^{\infty} s \cdot f_{S}(s) \cdot f_{T}(t) \cdot \mathbbm{1}_{s \in S} \ dadt} {P(S<T)}
\end{equation}

Similarly, we can find the standard deviation of the truncated stimulus movement onset distribution, where variance is the second moment, by:

\begin{equation}
    \sigma^2_{S_{react}} = \dfrac{\int_{-\infty}^{\infty}  \int_{-\infty}^{\infty} (s - \mu_{S_{react}})^2 \cdot f_{S}(s) \cdot f_{T}(t) \cdot \mathbbm{1}_{s<t} \ ds \ dt}{P(S<T)}
\end{equation}

The player’s movement onset distribution consists of a mix between reacting to the truncated stimulus movement onset and guessing. Importantly, reacting and guessing have unique delays and uncertainties. Thus, reaction decisions and guess decisions will lead to unique means and uncertainties of the participant movement onset distribution.
The participant mean reaction movement onset ($\mu_{mo_{react}}$, \textbf{Eq. 12}) is the truncated stimulus movement onset mean ($\mu_{S_{react}}$) plus the participant mean response time ($\mu_{rt}$). Likewise, the standard deviation of participant reaction movement onset (($\sigma_{mo_{react}}$, \textbf{Eq. 13}) is the square root of the variance of the truncated stimulus movement onset distribution ($\sigma_{A_{react}}$) plus the participant response time variance ($\sigma_{rt}^2$).

% Movement Onset times
\begin{equation}
    \mu_{mot_{react}} = \mu_{S_{react}} + \mu_{rt}
\end{equation}
\begin{equation}
    \sigma_{mot_{react}} = \sqrt{\sigma_{S_{react}}^2 + \sigma_{rt}^2}
\end{equation}

Here, $\mu_{rt}$ represents the time to process the stimulus movement plus the neuromechanical delay ($\mu_{nmd}$).
For the No Switch Time Model, the participant mean guess movement onset ($\mu_{mot_{guess}}$, \textbf{Eq. 14}) is the sum of the participant transition time $\tau$ and the mean neuromechanical delay $\mu_{nmd}$. The participant standard deviation guess movement onset ($\sigma_{mot_{guess}}$) is the square root of the sum of the timing variance $\sigma_{\tau}^2$ and neuromechanical delay variance $\sigma_{nmd}^2$ (\textbf{Eq. 15}).

\begin{equation}
    \mu_{mot_{guess}} = \tau +  \mu_{nmd}
\end{equation}
\begin{equation}
    \sigma_{mot_{guess}} = \sqrt{\sigma_{\tau}^2 + \sigma_{nmd}^2}
\end{equation}

Crucially, for the Known Switch Time Model and Unknown Switch Time Model, the mean and standard deviation of the guess movement onset includes the switch time mean and uncertainty,

% Switch time included in movement onset times
\begin{equation}
    \mu_{mot_{guess}} = \tau +  \mu_{nmd} + \mu_{switch}
\end{equation}
\begin{equation}
    \sigma_{mot_{guess}} = \sqrt{\sigma_{\tau}^2 + \sigma_{nmd}^2 + \sigma_{switch}^2}
\end{equation}

@@

We define the react target reach time mean ($\mu_{reach_{react}}$) and standard deviation ($\sigma_{reach_{react}}$), and the  guess target reach time mean ($\mu_{reach}{guess}$) and standard deviation ($\sigma_{reach_{guess}}$) as

% Target Reach Time 
\begin{align}
    \mu_{reach_{react}} =\mu_{mot_{react}} + \mu_{mt}                      \\
    \sigma_{reach_{react}} = \sqrt{\sigma_{mot_{react}}^2 + \sigma_{mt}^2} \\
    \mu_{reach_{guess}} =\mu_{mot_{guess}} + \mu_{mt}                      \\
    \sigma_{reach_{guess}} = \sqrt{\sigma_{mot_{guess}}^2 + \sigma_{mt}^2}.
\end{align}

To obtain the probability of reaching the target given the participant has either reacted ($X_{reach_{react}}$) or guessed ($X_{reach_{guess}}$), we need to define a random variable for the distribution of target reach times according to

% Reach random variables
\begin{align}
    X_{reach_{react}} \sim \mathcal{N}(\mu_{reach_{react}}, \sigma_{reach_{react}}) \\
    X_{reach_{guess}} \sim \mathcal{N}(\mu_{reach_{guess}}, \sigma_{reach_{guess}}) \\
    \hat{X}_{reach_{guess}} \sim \mathcal{N}(\hat{\mu}_{reach_{guess}}, \hat{\sigma}_{reach_{guess}}).
\end{align}

We can then define the probability that the participant will reach one of the two targets before the time constraint of 1500ms given they react ($P(Reach|React)$) or guess ($P(Reach|Guess)$):

% Probability of Reaching Target
\begin{align}
    P(Reach|React) = P(X_{reach_{react}} < 1500)
\end{align}
\begin{align}
    P(Reach|Guess) = P(X_{reach_{guess}} < 1500)
\end{align}

We can now define the conditional probabilities for three outcome metrics: indecision, win, and incorrect. The conditional probability of an indecision given the participant has reacted ($P(Indecision|React)$) or guessed ($P(Indecision|Guess)$) follows immediately from Eqs. 20-21. An indecision is simply the probability that the participant reaches the target after the time constraint:

% Probability of indecision sequence 
\begin{equation}
    P(Indecision|React) = 1 - P(Reach|React)
\end{equation}
\begin{equation}
    P(Indecision|Guess) = 1 - P(Reach|Guess)
\end{equation}

To define a win or incorrect trial, we need the conditional probability of selecting the correct target given the participant has either reacted ($P(Correct|React)$) or guessed ($P(Correct|Guess)$). The probability of selecting the correct target when the participant reacts is 100\% (\textbf{Eq. 24}). The probability of selecting the correct target when the participant guesses is 50\% (\textbf{Eq. 25}).

% Probability of being correct
\begin{equation}
    P(Correct|React) = 1.0
\end{equation}
\begin{equation}
    P(Correct|Guess) = 0.5
\end{equation}

The conditional probability the participant wins given they react ($P(Win|React)$) or guess ($P(Win|Guess)$) is the probability that they reach the target within the time constraint, and they select the correct target:

% Probability of winning sequence
\begin{equation}
    P(Win|React) = P(Reach|React) \cdot P(Correct|React)
\end{equation}
\begin{equation}
    P(Win|Guess) = P(Reach|Guess) \cdot P(Correct|Guess)
\end{equation}

The conditional probability the participant is incorrect given they react ($P(Incorrect|React)$) or guess ($P(Incorrect|Guess)$) is the probability that they reach the target within the time constraint and they select the wrong target:

% Probability of incorrect sequence 
\begin{equation}
    P(Incorrect|React) = P(Reach|React) \cdot (1 - P(Correct|React))
\end{equation}
\begin{equation}
    P(Incorrect|Guess) = P(Reach|Guess) \cdot (1 - P(Correct|Guess))
\end{equation}

Finally we define the final probability of wins ($P(Win|\tau)$), indecisions ($P(Indecision|\tau)$), and incorrects ($P(Incorrect|\tau)$), by considering their and their associated conditional probabilities (\textbf{Eq. 27-34}) and the probability of reaching and guessing given a transition time ($\tau$), as

\begin{align}
    P(Win|\tau)        = & P(React|\tau) \cdot P(Win|React) \nonumber        \\ &+  P(Guess|\tau) \cdot P(Win|Guess)\\
    P(Indecision|\tau) = & P(React|\tau) \cdot P(Indecision|React) \nonumber \\ &+ P(Guess|\tau) \cdot P(Indecision|Guess) \\
    P(Incorrect|\tau)  = & P(React|\tau) \cdot P(Incorrect|React) \nonumber  \\ &+ P(Guess|\tau) \cdot P(Incorrect|Guess).
\end{align}

@@

\noindent For each model, the goal of the decision policy is to find the optimal transition time that maximizes expected reward. The reward on a particular trial for wins ($R_{win}$), indecisions ($R_{indecision}$), and incorrects ($R_{incorrect}$) is,

% Expected Reward
\begin{equation}
    R_{win} = 1
\end{equation}
\begin{equation}
    R_{indecision} = 0
\end{equation}
\begin{equation}
    R_{incorrect} = 0
\end{equation}

The expected reward is defined as the reward of a trial outcome multiplied by the probability of that outcome, which is

\begin{align}
    \mathbb{E}[R|\tau] = & P(Win|\tau) \cdot R_{Win} \nonumber \\ &+ P(Incorrect|\tau) \cdot R_{Incorrect} \nonumber \\ &+ P(Indecision|\tau) \cdot R_{Indecision}
\end{align}

The decision policy uses known parameters to select an optimal transition time $\tau^*$ that maximizes expected reward:

% Maximize expected reward with tau
\begin{equation}
    \tau^* = \underset{\tau}{argmax}[\mathbb{E}(R|\tau)]
\end{equation}

\vspace{2mm}
\noindent\textbf{Model Parameter Estimation and Fitting Procedure}

>>>>

\newcommand{\SuppCaption}[2]{\noindent\textbf{{#1}} {#2}\footnotesize}
\newcommand{\SectionHeader}[1]{\noindent\textbf{\Large\textcolor{mydarkblue}{#1}}\normalsize }
\newcommand{\SubSectionHeader}[1]{\noindent\Large{\textcolor{mydarkblue}{#1}}\normalsize }

@@

@@

\noindent\boldblue{\large{Supplementary A: High Variance Results}}
\begin{figure}[H]
    \centering
    \includegraphics[scale =1]{figures/exp1_movement_onset_panel.png}
    \caption*{\boldblue{Supplementary Figure 1: Timing Behaviour.} \boldblue{A)} Average participant movement onset (y-axis) for each experimental condition (x-axis). We found a significant main effect of stimulus movement onset mean (F[1.55,29.48] = 4.36, p = 0.030) and variance (F[1.00,19.00], p = 0.017)) on participant movement onset. There was no significant interaction (F[1.66,31.47], p = 0.565) \boldblue{B)} Corresponding participant movement onset (y-axis) for the three different mean stimulus onsets (x-axis) when collapsed across variance. During the early mean conditions, participants had a high probability of reacting to the stimulus and reaching a target within the time constraint. For the middle mean conditions, participants often waited longer to react and had a later guess than the early mean conditions. Waiting longer to react and/or late guessing led to later movement onset. In the late mean condition, participants waited to react to the stimulus, but ended up guessing a majority of the time (see Supplementary Figure 6). The combination of waiting for the stimulus and eventually guessing, led to an earlier movement onset compared to the middle mean condition. For both the middle mean and late mean conditions, late guessing often led to indecisions (see \boldblue{Fig. 2}). \boldblue{C)} Participant movement onset standard deviation (y-axis) for each experimental condition (x-axis). We found a significant main effect of mean (F[1.38, 26.28], p = 0.018) and variance (F[1.00,19.00], p < 0.001) on participant movement onset standard deviation There was no significant interaction between stimulus movement onset mean and variance (F[1.98, 37.58], p = 0.097) \boldblue{D)} Corresponding participant movement onset standard deviation (y-axis) for the three different mean onsets (x-axis), when collapsed across variance. In the late mean conditions, waiting to react and then guessing led to a larger movement onset standard deviation compared to the early mean and middle mean conditions. Box and whisker plots display the 25th, 50th, and 75th percentiles. Open gray circles and connecting lines represent individual data.}
\end{figure}

\begin{figure}[H]
    \centering
    \includegraphics[scale = 1]{figures/exp1_score_metrics_panel.png}

    \caption*{\boldblue{Supplementary Figure 2: Trial Outcomes.} \boldblue{A)} Indecisions (\%) \boldblue{B)} Wins (\%), and \boldblue{C)} Incorrects (\%) for each condition. \boldblue{A)} We found that the middle mean low variance and \emph{late mean low variance} condition had a significantly greater number of indecisions compared to the \emph{early mean low variance} condition. That is, in the middle mean low variance and \emph{late mean low variance} conditions, participants often waited to react to the stimulus but ended up guessing late. These late guesses often led to indecisions. \boldblue{B)} Interestingly, we also found that the average win percentage (41\%) was significantly below the 50\% chance level (p < 0.001) in the \emph{late mean low variance} condition, clearly demonstrating suboptimal behaviour. Critically, participants would have earned more points if they had simply guessed early on all trials, rather than attempting to react to the stimulus. Collectively, these results show that participants were suboptimal decision makers that led to excessively indecisive behaviour.}
\end{figure}

\newpage
\noindent\boldblue{\large{Supplementary B: Optimal Models}}

We tested three different models to investigate the ability of participants to maximize reward during \boldblue{Experiment 1}: i) No Switch Time Model, ii) Full Switch Time Model and iii) Partial Switch Time Model (\boldblue{Fig. 2}). Each model represents a different hypothesis on how humans time their decisions, which we address further below. Intuitively, participants should react to the stimulus on trials where it moved earlier in time and guess on trials where it moved later in time. That is, reacting to early stimulus movement onsets ensures they can select the correct target. Likewise, guessing on late stimulus movement onsets affords the participant a 50\% chance of selecting the correct target. However, if participants wait too long to react to a late stimulus movement onset, then they might make too many indecisions and fail to maximize reward.
We modelled the time to switch from reacting to guessing as an optimal transition problem. This differs from past models that have used a similar Bayesian framework, which has beenused to determine reach aim \autocite{trommershauserStatisticalDecisionTheory2003} and reach timing \autocite{hudsonOptimalCompensationTemporal2008}. Here a model represents a decision-maker that selects a transition time, $\tau$. This transition time determines when to stop waiting to react to the stimulus and switch to guessing one of the two targets. The optimal transition time is determined from a decision policy that maximizes reward, given task constraints (i.e. stimulus movement onset distribution and time constraint), and knowledge of sensorimotor delays and uncertainties.

@@

\vspace{2mm}
\noindent \boldblue{General Formulation for the Models}

\noindent We begin by defining the general normal probability density function and cumulative density function:
\setlength{\belowdisplayskip}{4pt} \setlength{\belowdisplayshortskip}{4pt} % THIS MUST BE HERE FOR EQUATIONS SPACING
\setlength{\abovedisplayskip}{4pt} \setlength{\abovedisplayshortskip}{4pt}
% Define pdf and cdf
\begin{equation}
    X\sim\mathcal{N}(\mu,\sigma)
\end{equation}
\begin{equation}
    f_{X}(x; \mu, \sigma) = \frac{1}{\sigma\sqrt{2\pi}}e^{-\frac{1}{2}(\frac{x-\mu}{\sigma})^2}
\end{equation}
\begin{equation}
    F_{X}(b) = P(X \leq b) = \int_{-\infty}^{b} f_{X}(x; \mu, \sigma)dx
\end{equation}

@@

Next we define the mean and standard deviation of the participant movement onset separately for reaction decisions and guess decisions. We begin by defining $S$ as the random variable drawn from the stimulus’s movement onset distribution (\boldblue{Eq. 5}) and $T$ as the random variable drawn from the transition time distribution (\boldblue{Eq. 6}).
% Define random variables S and T
\begin{align}
    S & \sim\mathcal{N}(\mu_{S},\sigma_{S}) \\
    T & \sim\mathcal{N}(\tau,\sigma_{\tau})
\end{align}

Consider $s$ and $t$ as the realizations of random variables $S$ and $T$ for a single trial. On any specific trial, a decision-maker will react if the stimulus movement onset is before the transition time (i.e., $s<t$). Conversely, the decision-maker will guess at the transition time if the stimulus has not moved by the transition time (i.e., $s>t$). Thus, the probability that a participant will react or guess depends on the participants choice of a transition time $\tau$. Specifically, the probability that the participant will react is the probability that the random variable A is less than T.
% Define prob react and guess
\begin{equation}
    P(React|\tau) = P(T>S)
\end{equation}

Since the participants can only react or guess, the probability of guessing is simply one minus the probability of reacting.
\begin{equation}
    P(Guess|\tau) = P(T<S)
\end{equation}

As a result, a decision-maker only reacts to the portion of the stimulus’s distribution that is prior to their transition time. Thus, the participant reacts to a truncated distribution of the stimulus movement onset.
The truncated stimulus movement onset distribution is generated from only taking the random variable $S$ if it is less than the random variable $T$. We can then define an indicator function ($\mathbbm{1}_{s<t}$), which is equal to one if the realized value $s$ is less than $t$ and zero otherwise:
% Define indicator function 
\begin{align}
     & \mathbbm{1}_{s<t} =
    \begin{cases}
        1 & \text{if } s < t, \\
        0 & \text{otherwise.}
    \end{cases}
\end{align}

The mean of the truncated stimulus movement onset distribution ($\mu_{S_{react}}$) can be calculated by combining the indicator function and the method of moments. We start by calculating the expected value of the random variable $S$, which is the integral from $-\infty$ to $\infty$ of the value $s$ multiplied by the probability density function $f_{S}(s)$.
% Define expected value
\begin{equation}
    \mu_{S} = \mathbb{E}[S] = \int_{-\infty}^{\infty}s \cdot f_{S}(s)ds
\end{equation}

Note that the expected value of the full stimulus movement onset distribution defined here is equivalent to the mean of the distribution. For the truncated stimulus movement onset distribution, we only take values $s$ if they are less than $t$. Since the inclusion of $s$ depends on $t$, we calculate the mean of the truncated stimulus movement onset distribution by integrating over every possible combination of $s$ and $t$. Inside the double integral, we multiply the realized value $s$ by its probability density function (i.e., $f_{S}(s)$). We also multiply the probability density function for $t$ (i.e., $f_{T}(t)$) and the indicator function ($\mathbbm{1}_{s<t}$). Since this double integral multiplies two gaussian probability density functions and only sums values if $s$ is less than $t$, we must normalize by dividing by the probability that A is less than T. The mean (first moment) of the truncated stimulus movement onset distribution is
% Define Cutoff react mean 
\begin{equation}
    \mu_{S_{react}} = \dfrac{\int_{-\infty}^{\infty}  \int_{-\infty}^{\infty} s \cdot f_{S}(s) \cdot f_{T}(t) \cdot \mathbbm{1}_{s \in S} \ dadt} {P(S<T)}
\end{equation}

Similarly, we can find the standard deviation of the truncated stimulus movement onset distribution, where variance is the second moment, by:
%
\begin{equation}
    \sigma^2_{S_{react}} = \dfrac{\int_{-\infty}^{\infty}  \int_{-\infty}^{\infty} (s - \mu_{S_{react}})^2 \cdot f_{S}(s) \cdot f_{T}(t) \cdot \mathbbm{1}_{s<t} \ ds \ dt}{P(S<T)}
\end{equation}

The player’s movement onset distribution consists of a mix between reacting to the truncated stimulus movement onset and guessing. Importantly, reacting and guessing have unique delays and uncertainties. Thus, reaction decisions and guess decisions will lead to unique means and uncertainties of the participant movement onset distribution.
The participant mean reaction movement onset ($\mu_{mo_{react}}$, \boldblue{Eq. 14}) is the truncated stimulus movement onset mean ($\mu_{S_{react}}$) plus the participant mean response time ($\mu_{rt}$). Likewise, the standard deviation of participant reaction movement onset ($\sigma_{mo_{react}}$, \boldblue{Eq. 15}) is the square root of the variance of the truncated stimulus movement onset distribution ($\sigma_{A_{react}}$) plus the participant response time variance ($\sigma_{rt}^2$).
% Movement Onset times
\begin{equation}
    \mu_{mot_{react}} = \mu_{S_{react}} + \mu_{rt}
\end{equation}
\begin{equation}
    \sigma_{mot_{react}} = \sqrt{\sigma_{S_{react}}^2 + \sigma_{rt}^2}
\end{equation}

Here, $\mu_{rt}$ represents the time to process the stimulus movement plus the neuromechanical delay ($\mu_{nmd}$).
For the No Switch Time Model, the participant mean guess movement onset ($\mu_{mot_{guess}}$, \boldblue{Eq. 16}) is the sum of the participant transition time $\tau$ and the mean neuromechanical delay $\mu_{nmd}$. The participant standard deviation guess movement onset ($\sigma_{mot_{guess}}$) is the square root of the sum of the timing variance $\sigma_{\tau}^2$ and neuromechanical delay variance $\sigma_{nmd}^2$ (\boldblue{Eq. 17}).
%
\begin{equation}
    \mu_{mot_{guess}} = \tau +  \mu_{nmd}
\end{equation}
\begin{equation}
    \sigma_{mot_{guess}} = \sqrt{\sigma_{\tau}^2 + \sigma_{nmd}^2}
\end{equation}

Crucially, for the Known Switch Time Model and Unknown Switch Time Model, the mean and standard deviation of the guess movement onset includes the switch time mean and uncertainty,
% Switch time included in movement onset times
\begin{equation}
    \mu_{mot_{guess}} = \tau +  \mu_{nmd} + \mu_{switch}
\end{equation}
\begin{equation}
    \sigma_{mot_{guess}} = \sqrt{\sigma_{\tau}^2 + \sigma_{nmd}^2 + \sigma_{switch}^2}
\end{equation}

@@

We define the react target reach time mean ($\mu_{reach_{react}}$) and standard deviation ($\sigma_{reach_{react}}$), and the  guess target reach time mean ($\mu_{reach}{guess}$) and standard deviation ($\sigma_{reach_{guess}}$) as
% Target Reach Time 
\begin{align}
    \mu_{reach_{react}} =\mu_{mot_{react}} + \mu_{mt}                      \\
    \sigma_{reach_{react}} = \sqrt{\sigma_{mot_{react}}^2 + \sigma_{mt}^2} \\
    \mu_{reach_{guess}} =\mu_{mot_{guess}} + \mu_{mt}                      \\
    \sigma_{reach_{guess}} = \sqrt{\sigma_{mot_{guess}}^2 + \sigma_{mt}^2}.
\end{align}

To obtain the probability of reaching the target given the participant has either reacted ($X_{reach_{react}}$) or guessed ($X_{reach_{guess}}$), we need to define a random variable for the distribution of target reach times according to
% Reach random variables
\begin{align}
    X_{reach_{react}} \sim \mathcal{N}(\mu_{reach_{react}}, \sigma_{reach_{react}}) \\
    X_{reach_{guess}} \sim \mathcal{N}(\mu_{reach_{guess}}, \sigma_{reach_{guess}}) \\
    \hat{X}_{reach_{guess}} \sim \mathcal{N}(\hat{\mu}_{reach_{guess}}, \hat{\sigma}_{reach_{guess}}).
\end{align}

We can then define the probability that the participant will reach one of the two targets before the time constraint of 1500ms given they react ($P(Reach|React)$) or guess ($P(Reach|Guess)$):
% Probability of Reaching Target
\begin{align}
    P(Reach|React) = P(X_{reach_{react}} < 1500)
\end{align}
\begin{align}
    P(Reach|Guess) = P(X_{reach_{guess}} < 1500)
\end{align}

We can now define the conditional probabilities for three outcome metrics: indecision, win, and incorrect. The conditional probability of an indecision given the participant has reacted ($P(Indecision|React)$) or guessed ($P(Indecision|Guess)$) follows immediately from Eqs. 20-21. An indecision is simply the probability that the participant reaches the target after the time constraint:
% Probability of indecision sequence 
\begin{equation}
    P(Indecision|React) = 1 - P(Reach|React)
\end{equation}
\begin{equation}
    P(Indecision|Guess) = 1 - P(Reach|Guess)
\end{equation}

To define a win or incorrect trial, we need the conditional probability of selecting the correct target given the participant has either reacted ($P(Correct|React)$) or guessed ($P(Correct|Guess)$). The probability of selecting the correct target when the participant reacts is 100\% (\boldblue{Eq. 24}). The probability of selecting the correct target when the participant guesses is 50\% (\boldblue{Eq. 25}).
% Probability of being correct
\begin{equation}
    P(Correct|React) = 1.0
\end{equation}
\begin{equation}
    P(Correct|Guess) = 0.5
\end{equation}

The conditional probability the participant wins given they react ($P(Win|React)$) or guess ($P(Win|Guess)$) is the probability that they reach the target within the time constraint, and they select the correct target:
% Probability of winning sequence
\begin{equation}
    P(Win|React) = P(Reach|React) \cdot P(Correct|React)
\end{equation}
\begin{equation}
    P(Win|Guess) = P(Reach|Guess) \cdot P(Correct|Guess)
\end{equation}

The conditional probability the participant is incorrect given they react ($P(Incorrect|React)$) or guess ($P(Incorrect|Guess)$) is the probability that they reach the target within the time constraint and they select the wrong target:
% Probability of incorrect sequence 
\begin{equation}
    P(Incorrect|React) = P(Reach|React) \cdot (1 - P(Correct|React))
\end{equation}
\begin{equation}
    P(Incorrect|Guess) = P(Reach|Guess) \cdot (1 - P(Correct|Guess))
\end{equation}

Finally, we define the final probability of wins ($P(Win|\tau)$), indecisions ($P(Indecision|\tau)$), and incorrects ($P(Incorrect|\tau)$), by considering their and their associated conditional probabilities (\boldblue{Eq. 27-34}) and the probability of reaching and guessing given a transition time ($\tau$), as
\begin{align}
    P(Win|\tau)        = & P(React|\tau) \cdot P(Win|React) \nonumber        \\ &+  P(Guess|\tau) \cdot P(Win|Guess)\\
    P(Indecision|\tau) = & P(React|\tau) \cdot P(Indecision|React) \nonumber \\ &+ P(Guess|\tau) \cdot P(Indecision|Guess) \\
    P(Incorrect|\tau)  = & P(React|\tau) \cdot P(Incorrect|React) \nonumber  \\ &+ P(Guess|\tau) \cdot P(Incorrect|Guess).
\end{align}

@@

\noindent For each model, the goal of the decision policy is to find the optimal transition time that maximizes expected reward. The reward on a particular trial for wins ($R_{win}$), indecisions ($R_{indecision}$), and incorrects ($R_{incorrect}$) is,
% Expected Reward
\begin{equation}
    R_{win} = 1
\end{equation}
\begin{equation}
    R_{indecision} = 0
\end{equation}
\begin{equation}
    R_{incorrect} = 0
\end{equation}

The expected reward is defined as the reward of a trial outcome multiplied by the probability of that outcome, which is
%
\begin{align}
    \mathbb{E}[R|\tau] = & P(Win|\tau) \cdot R_{Win} \nonumber \\ &+ P(Incorrect|\tau) \cdot R_{Incorrect} \nonumber \\ &+ P(Indecision|\tau) \cdot R_{Indecision}
\end{align}

The decision policy uses known parameters to select an optimal transition time $\tau^*$ that maximizes expected reward:
% Maximize expected reward with tau
\begin{equation}
    \tau^* = \underset{\tau}{argmax}[\mathbb{E}(R|\tau)]
\end{equation}

\vspace{2mm}
\noindent\boldblue{Model Parameter Estimation and Fitting Procedure}
